\documentclass[12pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage[top=2cm, bottom=4cm, left=2cm, right=2cm]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{lastpage}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{siunitx}
\usepackage{appendix}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage{wrapfig}

\hypersetup{%
  colorlinks=true,
  linkcolor=blue,
  linkbordercolor={0 0 1}
}
 
\renewcommand\lstlistingname{Algorithm}
\renewcommand\lstlistlistingname{Algorithms}
\def\lstlistingautorefname{Alg.}

\lstdefinestyle{Python}{
    language        = Python,
    frame           = lines, 
    basicstyle      = \footnotesize,
    keywordstyle    = \color{blue},
    stringstyle     = \color{green},
    commentstyle    = \color{orange}\ttfamily
}

\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}

% Edit these as appropriate
\newcommand\course{ASTRO 732}
\newcommand\coursename{Computational Methods for Physics}
\newcommand\hwnumber{2}                  % <-- homework number
\newcommand\myname{Sandra Bustamante}           % <-- NetID of person #1

\pagestyle{fancyplain}
\headheight 35pt
\lhead{\course \\ Homework \hwnumber}
\chead{\textbf{\Large The Golfer and the Monkey}}
\rhead{\myname \\ September 20, 2019}
\lfoot{}
\cfoot{\coursename}
\rfoot{\small\thepage}
\headsep 1.5em

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%=====================BEGIN DOCUMENT===========================
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{The Golfer and the Monkey}

\begin{document}
%\twocolumn

\begin{quote}
    \textit{A monkey has been stealing your bananas everyday for a month now. You are thinking what can you do to resolve this problem on your way to golf practice. Suddenly, you see something moving on a tree. It's HIM. On closer inspection, he looks like he is waiting for you to leave your house and steal your fresh bananas. 'No way!' you think and decide to scare the monkey away from your fruit. You prepare to shoot at him your golf ball. You estimate he is at about \SI{2000}{\m} away at a height of, probably, \SI{60}{\m}. What angle will you shoot?}
\end{quote}

\input{problem2-1.tex}
\input{problem2-2.tex}
\input{problem2-3.tex}
%\include{name} %name without extension. insert in new page

\newpage
\appendix

\lstset{caption={hw02.py}, style=Python}

\section[]{Python code to solve Homework 2} 
\label{sec:CodeHw02}
\lstset{label={hw02.py}}
\lstinputlisting[language=Python]{hw02.py}


% \newpage
% \section[]{Python Code to Solve Problem 5} 
% \label{sec:CodeHw01-5}
% \lstset{label={hw01prob1-5.py}}
% \lstinputlisting[language=Python]{code/hw01prob1-5.py}

\end{document}